### 2020-06-18 chapters/my-work.tex
...

\subsubsection*{Multiple Test Correction}
Note that we periodically apply this test (Equation \ref{eq:alert-test}) for each feature, effectively repeating the analysis. When considering several hypotheses, the problem of multiplicity arises: the more hypotheses are checked, the higher the probability of obtaining false positives. In other words, when repeating a test multiple times the multiple test problem arises which states that the more inferences are made, the more likely erroneous inferences are to occur. In the literature, many multiple test correction methods are proposed, but we opt to use the Holm-Bonferroni multiple test correction. The Holm-Bonferroni method is one of many approaches for controlling the so called Family-Wise Error Rate \textit{(FWER)} by adjusting the rejection criteria for each hypothesis.

\subsubsection*{Holm-Bonferroni Correction}
The Holm-Bonferroni correction takes Equation \ref{eq:alert-test} and corrects the right-side threshold $\alpha$ for each feature. This correction is done by dividing the threshold $\alpha$ by a correction factor, as described below.

>>>>

\subsubsection*{Multiple Test Correction} \label{sec:multi-test}
Note that we periodically apply this test (Equation \ref{eq:alert-test}) for each feature, effectively repeating the analysis. When considering several hypotheses, the problem of multiplicity arises: the more hypotheses are checked, the higher the probability of obtaining false positives. In other words, when repeating a test multiple times the multiple test problem arises which states that the more inferences are made, the more likely erroneous inferences are to occur. In the literature, many multiple test correction methods are proposed, but we opt to use the Holm-Bonferroni multiple test correction. The Holm-Bonferroni method is one of many approaches for controlling the so called Family-Wise Error Rate \textit{(FWER)} by adjusting the rejection criteria for each hypothesis.

\subsubsection*{Holm-Bonferroni Correction} \label{sec:holmbonferroni}
The Holm-Bonferroni correction takes Equation \ref{eq:alert-test} and corrects the right-side threshold $\alpha$ for each feature. This correction is done by dividing the threshold $\alpha$ by a correction factor, as described below.

### 2020-06-18 chapters/validation.tex
Real-Time Stream Anomaly Detection with Hierarchical Temporal Memory (HTM)
...

\section{Datasets description}
\subsection{Synthetic datasets}
\subsection{Financial fraud datasets}

\section{Tests description}
\subsection{Single feature}
\subsection{Multi feature}

\section{Tests results}
\subsection{Single feature}
\subsection{Multi feature}

>>>>

\section{Datasets}

% 01: 
    % ref: N(10,2) for 5M
    % target: N(10,2) for 2.5M and U(100,200) after for 2.5M

% 02:
% 03:
% 04:
% 05:
% 06:

We generated multiple synthetic datasets before moving on to real data. Furthermore, we first performed single feature analysis before moving to a multi-feature scenario. The problem of multiple testing (Section \ref{sec:multi-test}) only arises in the latter case so we only apply the Holm-Bonferroni correction (Section \ref{sec:holmbonferroni}) for that one.

\subsection{Synthetic datasets}
For each test we generated two datasets: one to be used by our method as the reference period and the other as the target or streaming period.

\subsubsection*{Reference and Target Datasets 01}
The Reference Dataset 01 (RD01) contained 5 million events each with a single feature \emph{x1} that followed a normal distribution with mean $\mu=10$ and $\sigma=2$. The Target Dataset 01 (TD01) was also made up of 5 million events each with a single feature. For the first half of the dataset, \textit{i.e.}, for the first 2.5 million events, similarly to the reference dataset, the feature followed a normal distribution with mean $\mu=10$ and $\sigma=2$. However, for the other half, the last 2.5 million events, we changed the generating distribution to be a continuous uniform one with $a=100$ and $b=200$.

\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{figures/01-reference.png}
  \captionof{figure}{Reference dataset 01 (RD01)}
  \label{fig:rd01}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{figures/01-target.png}
  \captionof{figure}{Target dataset 01 (TD01)}
  \label{fig:td01}
\end{minipage}

\subsection{Financial fraud datasets}

\section{Experimental Setup}
\subsection{Single feature}
\subsection{Multi feature}

\section{Results}
\subsection{Single feature}
\subsection{Multi feature}
